Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-09-16 analysis/analyse_rnaseq1.Rmd
add quantiles

mg$size <- as.numeric(sapply(strsplit(mg$BgRatio.x,"/"),"[[",1))
quantiles <- quantile(mg$size, prob = seq(0, 1, length = 6), type = 5)
mg$levels <- cut2(mg$size, cuts = as.numeric(quantiles))
cols <- gsub("5","red",gsub("4","orange",gsub("3","yellow",gsub("2","green",gsub("1","blue",as.character(as.numeric(mg$levels)))))))

>>>>

mg$size <- as.numeric(sapply(strsplit(mg$BgRatio.x,"/"),"[[",1))
quantiles <- quantile(mg$size, prob = seq(0, 1, length = 6), type = 5)
quantiles
mg$levels <- cut2(mg$size, cuts = as.numeric(quantiles))
cols <- gsub("5","red",gsub("4","orange",gsub("3","yellow",gsub("2","green",gsub("1","blue",as.character(as.numeric(mg$levels)))))))
